\question Find the path from the start, $S$, to the goal, $G$, when running
each of the following algorithms.

The \define{heuristic}, $h$, estimates the distance from each node to the goal.

\begin{center}
\begin{tikzpicture}[scale=0.15]
\tikzstyle{every node}+=[inner sep=0pt]
\draw (60,-15) circle (3);
\draw (60,-15) node {$E$};
\draw (66.5,-15) node {\footnotesize $h = 1$};
\draw (10,-30) circle (3);
\draw (10,-30) node {$S$};
\draw (15,-33) node {\footnotesize $h = 6$};
\draw (30,-30) circle (3);
\draw (30,-30) node {$A$};
\draw (35,-33) node {\footnotesize $h = 5$};
\draw (30,-45) circle (3);
\draw (30,-45) node {$B$};
\draw (35,-48) node {\footnotesize $h = 6$};
\draw (55,-30) circle (3);
\draw (55,-30) node {$D$};
\draw (60,-33) node {\footnotesize $h = 2$};
\draw (70,-30) circle (3);
\draw (70,-30) node {$G$};
\draw (75,-33) node {\footnotesize $h = 0$};
\draw (10,-45) circle (3);
\draw (10,-45) node {$C$};
\draw (15,-48) node {\footnotesize $h = 7$};
\draw (13,-30) -- (27,-30);
\fill (27,-30) -- (26.2,-29.5) -- (26.2,-30.5);
\draw (20,-29.5) node [above] {$1$};
\draw (30,-33) -- (30,-42);
\fill (30,-42) -- (30.5,-41.2) -- (29.5,-41.2);
\draw (29.5,-37.5) node [left] {$1$};
\draw (27,-45) -- (13,-45);
\fill (13,-45) -- (13.8,-45.5) -- (13.8,-44.5);
\draw (20,-44.5) node [above] {$1$};
\draw (33,-30) -- (52,-30);
\fill (52,-30) -- (51.2,-29.5) -- (51.2,-30.5);
\draw (42.5,-29.5) node [above] {$3$};
\draw (32.68,-28.66) -- (57.32,-16.34);
\fill (57.32,-16.34) -- (56.38,-16.25) -- (56.82,-17.15);
\draw (44.04,-22) node [above] {$8$};
\draw (59.05,-17.85) -- (55.95,-27.15);
\fill (55.95,-27.15) -- (56.68,-26.55) -- (55.73,-26.24);
\draw (56.73,-21.8) node [left] {$1$};
\draw (58,-30) -- (67,-30);
\fill (67,-30) -- (66.2,-29.5) -- (66.2,-30.5);
\draw (62.5,-29.5) node [above] {$2$};
\draw (61.66,-17.5) -- (68.34,-27.5);
\fill (68.34,-27.5) -- (68.31,-26.56) -- (67.48,-27.12);
\draw (64.39,-23.83) node [left] {$1$};
\end{tikzpicture}
\end{center}

\begin{solution}
Note that uniform cost search and greedy search are not a part of the course.
The algorithms for all 3 of these searches are extremely similar, the only
difference being the priority given to each node and whether or not we need to
keep track of the cumulative distance to a vertex.
\end{solution}

\begin{parts}
\part Which path does uniform cost search return?

\define{Uniform cost search} is the same as Dijkstra's, except that the search
stops once we visit the goal state.

\begin{solution}[1in]
$S - A - D - G$

From the starting node, choose the path that has the least cost, go to that
node, and repeat until we reach the goal node. We choose the lowest
\emph{backward cost}.

We keep a priority-queue fringe that keeps track of paths. At each step, we
remove the shortest path from the fringe and add its children to the fringe,
trying all paths in increasing cost order until we reach $G$.
\end{solution}

\part Which path does greedy search return?

In \define{greedy search}, we ignore edge weights entirely and only use the
heuristic to decide which node to visit next.

\begin{solution}[1in]
$S - A - E - D - G$

From the starting node, travel to the next node with the lowest value returned
by the heuristic function until we reach the goal node. We choose the path with
the lowest \emph{forward cost}.

Note that, unlike UCS or Dijkstra's, we don't add heuristics together because
they already estimate the distance to the goal.
\end{solution}

\part Which path does A* search return?

\define{A* search} is an algorithm that combines the total distance from the
start with the heuristic to optimize the search procedure.

\begin{solution}[1in]
$S - A - D - G$

At each node, we choose the next node that has the lowest sum of the path cost
and $h(\cdot)$ value. This is essentially uniform cost search and greedy search
combined.

For A* to work, heuristics must be \emph{admissible} and \emph{consistent}.

\begin{itemize}
\item Admissible heuristics underestimate the true distance to the goal.
\item Consistent heuristics require that the difference in heuristic values
between two nodes cannot be greater than the true distance between the two.
\end{itemize}
\end{solution}
\end{parts}
