\question Below, the \textbf{leftmost column} is an unsorted list of strings. The \textbf{rightmost column} gives the same strings in sorted order. Each of the remaining columns gives the contents of the list during some intermediate step of one of the algorithms listed below. Match each column with its corresponding algorithm.

\begin{inparaitem}[$\cdot$]
\item Merge sort
\item Quicksort
\item Heap sort
\item LSD radix sort
\item MSD radix sort
\end{inparaitem}

For quicksort, choose the topmost element as the pivot. Use the recursive (or top-down) implementation for merge sort.

{
\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{12pt}
\begin{ttfamily}
\begin{tabular}{r|ccccccc}
   & A    & B    & C    & D    & E    & F    & G    \\\hline
1  & 4873 & 1876 & 1874 & 1626 & 9573 & 2212 & 1626 \\
2  & 1874 & 1874 & 1626 & 1874 & 7121 & 8917 & 1874 \\
3  & 8917 & 2212 & 1876 & 1876 & 9132 & 7121 & 1876 \\
4  & 1626 & 1626 & 1897 & 4873 & 6973 & 1626 & 1897 \\
5  & 4982 & 3492 & 2212 & 4982 & 4982 & 9132 & 2212 \\
6  & 9132 & 1897 & 3492 & 8917 & 8917 & 6152 & 3492 \\
7  & 9573 & 4873 & 4873 & 9132 & 6152 & 4873 & 4873 \\
8  & 1876 & 9573 & 4982 & 9573 & 1876 & 9573 & 4982 \\
9  & 6973 & 6973 & 6973 & 1897 & 1626 & 6973 & 6152 \\
10 & 1897 & 9132 & 6152 & 3492 & 1897 & 1874 & 6973 \\
11 & 9587 & 9587 & 7121 & 6973 & 1874 & 1876 & 7121 \\
12 & 3492 & 4982 & 8917 & 9587 & 3492 & 9877 & 8917 \\
13 & 9877 & 9877 & 9132 & 2212 & 4873 & 4982 & 9132 \\
14 & 2212 & 8917 & 9573 & 6152 & 2212 & 9587 & 9573 \\
15 & 6152 & 6152 & 9587 & 7121 & 9587 & 3492 & 9587 \\
16 & 7121 & 7121 & 9877 & 9877 & 9877 & 1897 & 9877
\end{tabular}
\end{ttfamily}
}

\begin{solution}
From left to right: unsorted list, quicksort, MSD radix sort, merge sort, heap sort, LSD radix sort, completely sorted.

\begin{description}
\item[MSD] Look at the left-most digits. They should be sorted. Mark this immediately as MSD.
\item[LSD] One of the digits should be sorted. Start by looking at the right most digit of the remaining sorts. Then check the second from right digit of the remaining sorts and so on. As soon as you find one in which at least something is sorted, mark that as LSD.
\item[Heap] Max-oriented heap so check that the bottom is in sorted order and that the top element is the next max element.
\item[Merge] Realize that the first pass of merge sort fixes items in groups of 2. Identify the passes and look for sorted runs.
\item[Quick] Run quicksort using the pivot strategy outlined above. Look for partitions and check that 4873 is in its correct final position.
\end{description}
\end{solution}