\begin{blocksection}
\question Given a weighted, directed graph $G$ where the weights of every edge
in $G$ are all integers between 1 and 10, and a starting vertex $s$ in $G$,
find the distance from $s$ to every other vertex in the graph where the
distance between two vertices is defined as the weight of the shortest path
connecting them, or infinity if no such path exists.

\begin{parts}
\part Design an algorithm for solving the problem that runs faster than
Dijkstra's.
\begin{solution}[2in]
For every edge $e$ in the graph, replace $e$ with a chain of $w-1$ vertices
(where $w$ is the weight of $e$) where the two ends of the chain are the
endpoints of $e$.

Then run BFS on the modified graph, keeping track of the distance from $v$ to
each vertex from the original graph.

Alternatively, we can modify Dijkstra's algorithm. Since the runtime of
Dijkstra's is bounded by the priority queue implementation, if we can come up
with a faster priority queue, we can improve the runtime. Define our priority
queue as an array of 11 linked list buckets. Keep track of a counter that
represents our current position in the array. Each bucket corresponds to
vertices of some distance from the start, $s$.

\lstinline$removeMin()$: If the bucket with index counter is non-empty, remove
and return the first vertex in its linked list. Otherwise, increment counter
until we find a non-empty bucket. If the counter reaches 11, reset it to 0 and
continue (so in effect our array is circular).

\lstinline$insert()$: Given a vertex $v$ and a distance $d$, insert the vertex
into the beginning of the linked list at index $d \mod 11$.

This strategy works because the vertices we add to the priority queue at any
time have a distance that is no more than 10 greater than the current distance.
\end{solution}

\part Give the runtime of your algorithm.
\begin{solution}[0.5in]
$\Theta(|V| + |E|)$ for running BFS on the modified graph, and $O(|V| + |E|)$
for modifying Dijkstra's priority queue.
\end{solution}
\end{parts}
\end{blocksection}
